---
title: "Developing Data Products"
subtitle: "Final Projct - Cumulative Stock Return Analysis"
author: "Anthony Lei"
date: "December 26, 2016"
output: ioslides_presentation
framework: io2012
highlighter: highlight.js
widgets: [mathjax, quiz, bootstrap]
mode: selfcontained
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application Overiew & Motivation
There are quite a few website provide financial information of public traded companies, for example google finance, finviz.com. They are great at sharing a snapshot of a company's current financial information and historical price, however, often times, lack of comparision to benchmark and historical performance in terms of returns. This application focus on comparing the cumulative return of a public traded company to it's benchmark ex, S&P 500 index/ETF. The application clearly visualizes the stock performance of a company and its benchmark.

Individual stock & Benchmark - Return Analysis:
<http://returns.shinyapps.io/ShinyApp/>.

## Application Input:

- Ticker: The stock quote to analyze (It only takes US publicaly traded companies.)
- Benchmark: The compirasion, often times, S&P 500 is used to compare large cap companies (market capitalization larger than $5 billion.)
- Start Date: the first day of the comparision.
- End Date: the last day of the comparision.

## Application Output:

- Cumulative Return: Discrete cumulative percentage return of the invesment, ex, 1 equals to 100% return.
- Daily Return: Percentage return per day
- Drawdown: Percentage (negative) return since the lastest new high.


## Application Requirement for local deployment:

Please make sure quantmod and PerformanceAnalytics is installed.
```{r echo = TRUE, comment=NA, message= FALSE, warning=FALSE, error=FALSE}
library(quantmod)
library(PerformanceAnalytics)
```

## Acknowledgement
Thank Ryan etal. for building quantmod and Peterson etal. for building PerformanceAnalytics. Without their fabulous packages, this application would not have been possible.
